Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-10-23 Methods-and-Results.Rmd
code hide fix

\subsection{Contact key need content}
topic model

>>>>

\subsection{Contact key need content}

Because our participants jointly reported on several thousands of intergroup contacts, it would not be feasible to analyse these qualitative responses in a traditional qualitative content analysis. We instead rely on recent machine learning advances within the natural language processing domain. For our analysis we use the BERT language model. BERT (Bidirectional Encoder Representations from Transformers) was developed by Google in 2018 and today forms a key elements of many natural language processing workflows. In its essence, BERT is a framework that allows users to codify every word in relation to every other word within a large set of documents. This task is immensely computationally intensive and most users of the framework don't create their own model. We use the "all-mpnet-base-v2" language model for our embedding. The model is a community-based version of BERT that uses Microsoft's "mpnet-base" model and is fine-tuned with 1 Billion diverse sentence pairs. The model was trained with a 768 dimensional dense vector space (a relatively high number) to represent every word. As a result, the model is widely considered to be one of the most accurate all-purpose language models within the open-source BERT framework. We extracted 47 topics from the 2,983 interaction goal free-text entries --- a relatively large number of topics. The higher number of topics allows us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (16.64%). A full write up of the topic modeling process is available in Online Supplemental Material C.

In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance. Opposing the task and work oriented needs, are a wide variety of leisure-related wishes. Specifically, relaxation and entertainment wishes were prominent terms across several topics. Additionally, a number of clusters is primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself. Similarly, socializing and celebrations were also explicit social needs (incl., parties). Another set of topics was more practically oriented, when participants sought to share food and cook cook together, or had organizational needs (e.g., housing, cleaning, and living).

A reasonable set of contact goals were specifically migration specific (e.g., wish to learn about culture, politics, and language) or were concerned inquiry and information needs more generally (e.g., seeking answers, banking information). A further set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food). Similarly, a number of participants had travel related goals in their interactions with the majority group members.

One interesting observation was the importance of contact goals specific to contact through the medical and public health system. This goal type was partly specific to our young medical professionals sample (e.g., working with patients, treatment), but also more broadly interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals). Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members. A final also under-explored topic is that of spiritual, religious, and otherwise transcendental needs (incl. meditation, prayer, religious services). This seems to offer a deep and fundamental need that is mostly ignored in western secular migrant research.

Thus while, medical and spiritual interaction goals were more unexpected, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature. Something about need theories/models plus our own review article.

### 2022-10-23 Methods-and-Results.tex
code hide fix

topic model

>>>>

Because our participants jointly reported on several thousands of
intergroup contacts, it would not be feasible to analyse these
qualitative responses in a traditional qualitative content analysis. We
instead rely on recent machine learning advances within the natural
language processing domain. For our analysis we use the BERT language
model. BERT (Bidirectional Encoder Representations from Transformers)
was developed by Google in 2018 and today forms a key elements of many
natural language processing workflows. In its essence, BERT is a
framework that allows users to codify every word in relation to every
other word within a large set of documents. This task is immensely
computationally intensive and most users of the framework don't create
their own model. We use the ``all-mpnet-base-v2'' language model for our
embedding. The model is a community-based version of BERT that uses
Microsoft's ``mpnet-base'' model and is fine-tuned with 1 Billion
diverse sentence pairs. The model was trained with a 768 dimensional
dense vector space (a relatively high number) to represent every word.
As a result, the model is widely considered to be one of the most
accurate all-purpose language models within the open-source BERT
framework. We extracted 47 topics from the 2,983 interaction goal
free-text entries --- a relatively large number of topics. The higher
number of topics allows us to retain more of the smaller topics and
leaves a relatively low number of 308 free-text entries unclassified
(16.64\%). A full write up of the topic modeling process is available in
Online Supplemental Material C.

In terms of the content of the topics, we find that a number of topics
are primarily task-oriented, where participants hope to increase their
study, research, presentation, or work performance. Opposing the task
and work oriented needs, are a wide variety of leisure-related wishes.
Specifically, relaxation and entertainment wishes were prominent terms
across several topics. Additionally, a number of clusters is primarily
relationship-oriented, so that participants sought contact with outgroup
members for intimate and casual social contact in itself. Similarly,
socializing and celebrations were also explicit social needs (incl.,
parties). Another set of topics was more practically oriented, when
participants sought to share food and cook cook together, or had
organizational needs (e.g., housing, cleaning, and living).

A reasonable set of contact goals were specifically migration specific
(e.g., wish to learn about culture, politics, and language) or were
concerned inquiry and information needs more generally (e.g., seeking
answers, banking information). A further set of topics was specifically
geared towards a wish to experience cultural products (e.g., music,
theater, food). Similarly, a number of participants had travel related
goals in their interactions with the majority group members.

One interesting observation was the importance of contact goals specific
to contact through the medical and public health system. This goal type
was partly specific to our young medical professionals sample (e.g.,
working with patients, treatment), but also more broadly interactions of
newcomers with the outgroup majority as patients themselves (e.g.,
therapeutic goals). Also health, fitness, and personal improvement goals
(e.g., sports and music) were common goals that participants shared
during the interactions with the majority group members. A final also
under-explored topic is that of spiritual, religious, and otherwise
transcendental needs (incl.~meditation, prayer, religious services).
This seems to offer a deep and fundamental need that is mostly ignored
in western secular migrant research.

Thus while, medical and spiritual interaction goals were more
unexpected, almost all other extracted topics fall into broader or
narrower need concepts that are commonly discussed within the
psychological needs literature. Something about need theories/models
plus our own review article.
